---
title: "HW_2"
author: "MGinorio"
date: "2/14/2021"
output: html_document
---

## Assignment # 2

** Choose six recent popular movies. 
** Ask at least five people that you know (friends, family, classmates, imaginary friends if necessary) to rate each of these movies that they have seen on a scale of 1 to 5. 
** Take the results (observations) and store them in a SQL database of your choosing. Load the information from the SQL database into an R dataframe.


```{r}
# install packages RmySQL
library(RMySQL)
library(dplyr)
library(ggplot2)
library(psych)
library(dotenv)
# establish connection with MySQL


```
## sTEP 2. SETTINGS

```{r}
db_user       <- "root"
db_password   <- "newrootpassword"
db_name       <- "movies_db"
db_table      <- "friends_info"
db_host       <- "localhost"
db_port       <-  3306

```

## Connect to the MySql database and retrieve the data:


```{r}
myConnection <- dbConnect(MySQL(), user = db_user, password = db_password,
                          dbname = db_name, host = db_host, port = db_port)
```

## Use survey software to gather the information.
Google form/ survey used for collecting data added to Repository

## Are you able to use a password without having to share the password with people who are viewing your code?

One of the most interesting approaches i found by the research is to create a .env file and save the password there. The file .env has been added to the gitignore file in github.

## While it’s acceptable to create a single SQL table, can you create a normalized set of tables that corresponds to the relationship between your movie viewing friends and the movies being rated?

I created 4 different set of tables each one of them with a primary key.
** Friends_info > indicates Friend_ID, Name, Genre
** Friends_ Rating > indicates the value each movie has been given.
** Movie_ ID > indicates the movie name and genre
**Movie_ratings > the overall ratings from all the participants in the survey

## Creating a query connected to MySQL

```{r}
query <- 'Select Friend ID, Name, Gender from Friends_info'

```

## Obtain Data from csv in github
```{r}
movies_info <-read.csv("https://raw.githubusercontent.com/mgino11/SQL_likert/main/Movie_ID.csv")

glimpse(movies_info)
```
```{r}
movies_info %>%
  count(Movie_genre) %>%
  arrange(desc(n))
```
## Is there any benefit in standardizing ratings? How might you approach this?
it is definitively a better approach to make variables easier to interpret data easier.Usually, standardization refers to the process of subtracting the mean and dividing by the standard deviation. 

```{r}
movies_ratings <-read.csv("https://raw.githubusercontent.com/mgino11/SQL_likert/main/Friends_rating.csv")

glimpse(movies_ratings)
```
```{r}
movies_ratings_df <- as.data.frame(movies_ratings)
movies_ratings_df
```

## Atemp to graph the Data using Likert Package
```{r}
library(likert)
my_levels <- c("Stongly Disliked",
               "Disliked",
               "Neutral",
               "Liked",
               "Strongly Liked")

movies_ratings_df <- movies_ratings_df %>%
  mutate( "Strongly Disliked" = factor("Strongly Disliked",
                                       levels = my_levels),
          "Disliked" = factor("Disliked",
                              levels  = my_levels),
          "Neutral" = factor("Neutral",
                             levels = my_levels),
          "Liked" = factor("Liked", 
                           levels = my_levels),
          "Strongly Liked" = factor("Strongly Liked",
                                    levels = my_levels))

movie_ratings <- likert(movies_ratings_df)
```

